MaxEnt: What is it good for?

### 2015-06-19 ms.tex
constraint rule

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

@@

>>>>

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values.

 Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

@@

\subsection{The ``constraint rule'' controversy}
Is it valid to use an experimental average (literally the arithmetic mean of
some data) to set the expected value of a probability distribution? The
assumption that this is okay has been termed {\it the constraint rule}.

In many presentations of MaxEnt, it is assumed that this is not a problem
({\bf cite people}). Other authors have noticed that it's possible to
condition on the observed arithmetic mean, as one would do in a standard
Bayesian analysis of that information, and that this can lead to a different
answer from the constraint rule.
